\LARGE \bf An Overview of reinforcement learning

### 2020-07-15 paper/paper.tex
Add use cases

@@

\todo{todo}

\section{Examples of use cases}

\todo{todo}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.

>>>>

\subsection{REINFORCE}

@@

\subsection{Resources Management in Computer Clusters}

Designing algorithms to allocate limited resources to different tasks
is challenging and requires human-generated
heuristics. In~\cite{mao2016resource} the authors showed how to use RL
to automatically learn to allocate and schedule computer resources to
waiting jobs, with the objective to minimize the average job slowdown.

They formulated the state space as the current resources allocation
and the resources profile of jobs. For action space, they used a trick
to allow the agent to choose more than one action at each time
step. Reward was the sum of $-1/duration\_of\_the\_job$ over all the
jobs in the system. Then they combined REINFORCE algorithm and
baseline value to calculate the policy gradients and find the best
policy parameters that give the probability distribution of actions to
minimize the objective. See
\href{https://github.com/hongzimao/deeprm}{this repository} for the
implentation.

\subsection{Traffic Light Control}

In~\cite{arel2010reinforcement}, researchers tried to design a traffic
light controller to solve the congestion problem. Tested only on
simulated environment though, their methods showed superior results
than traditional methods and shed a light on the potential uses of
multi-agent RL in designing traffic system.

They put five agents in the five-intersection traffic network, with an
agent at the central intersection to control traffic signaling. The
state was defined as an eight-dimensional vector with each element
representing the relative traffic flow of each lane. Eight choices
were available to the agent, each representing a phase combination,
and they defined the reward function as a reduction in the delay
compared with earlier time step. The authors used DQN to learn the Q
value of the {state, action} pairs.

\subsection{Robotics}

Robotics is an area where reinforcement learning has shown a lot of
promise. A general survey can be found
in~\cite{kober2013reinforcement}. In particular,~\cite{levine2016end}
trained a robot to learn policies to map raw videno images to the
robot’s actions. They fed the RGB images to a CNN and outputs were the
motor torques. The RL component was the guided policy search to
generate training data that came from its own state distribution.

\subsection{Personalized Recommendations}

Previous work of news recommendations faced several challenges
including the changing dynamic of news, users get bored and Click
Through Rate cannot show the retention rate of users. Guanjie et
al.~have applied RL in news recommendation system to combat the
problems in~\cite{zheng2018drn}.

They constructed four categories of
features:
\begin{itemize}
	\item User features
	\item Context features as the state features of the environment
	\item User-news features
	\item News features as the action features.
\end{itemize}

The four features were input to the Deep Q-Network (DQN) to calculate
the Q-value. The agent chose a list of news to recommend based on the
Q-value, and the user’s click on the news was a part of the reward the
RL agent received.

\subsection{Bidding and Advertising}

Researchers from Alibaba Group published~\cite{jin2018real} and
claimed that their distributed cluster-based multi-agent bidding
solution (DCMAB) has achieved promising results and thus they plan to
conduct a live test in Taobao platform.

Taobao ad platform is a place for merchants to place a bid
to display ad to the customers. This could be a multi-agent problem
because the merchants are bidding against each other and their actions
are interrelated. In the paper, merchants and customers were clustered
into different groups to reduce computational complexity. The state
space of the agents showed the cost-revenue status of the agents,
action space was the bid (continuous), and reward was the revenue
caused by the customer cluster.

\subsection{Games}

RL is so well known these days because it is the mainstream algorithm
used to solve different games and sometimes achieve superhuman
performance.

The most famous one must be AlphaGo~\cite{silver2016mastering} and
AlphaGo Zero~\cite{silver2017alphago}. AlphaGo, trained with countless
human games, already achieved superhuman performance by using value
network and Monte Carlo tree search (MCTS) in its policy network. Yet,
the researchers later on thought back and tried a purer RL approach —
train it from scratch. The researchers let the new agent, AlphaGo
Zero, played with itself and beat AlphaGo 100–0.

\subsection{Deep Learning}

More and more attempts to combine RL and other deep learning
architecture can be seen, and they showed impressive results.

One of the most influential work in RL is the pioneering work of
DeepMind to combine CNN with RL~\cite{minh_dqn}. By doing so, the
agent can “see” the environment through high-dimensional sensory and
then learn to interact with it.

RL and RNN is another combinations people used to try a novel
idea. RNN is a neural network that has “memories”. When joint with RL,
RNN gives the agents’ ability to memorize things. For
example,~\cite{hausknecht_2015} joint LSTM with RL to create Deep
Recurrent Q-Network (DRQN) to play Atari 2600
games. In~\cite{zhou2017optimizing} the authors also used RNN and RL
to solve chemical reaction optimization problem.

DeepMind showed~\cite{ganin_2018} how to use generative models and RL to generate
programs. In the model, the adversarially trained agent used the
signal as rewards to improve the actions, instead of propagating the
gradients to the input space as in the GAN training.

\addtolength{\textheight}{-12.5cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.
